---
title: "STATS509_HW10"
author: "Xiaoxue Xin"
date: "4876 5091"
output:
  word_document: default
  html_document:
    df_print: paged
---

## 1.(1)

```{r}
DATA = read.csv("NYA-2015-2017.csv", header = TRUE)
NYSE_lret = diff(log(DATA$Adj.Close))
NYSE_lret.ts = ts(data = NYSE_lret, start = c(2015,1), frequency = 252, names = c('logret'))
library(fGarch)
model = garchFit(formula = ~ garch(1,1), data = NYSE_lret.ts)
summary(model)
lambda = 1.752e-01 + 7.800e-01
1 - log(2)/log(lambda)
```

The standard error of αo, α1, β1 are 9.672e-07, 3.761e-02, and 4.316e-02. We take k, half life of volatility, to be 17.

## (2)


```{r}
plot(volatility(model), type = 'l')
plot(model@residuals, type = 'l')
```

## (3)


```{r}
qqnorm(model@residuals/model@sigma.t)
qqline(model@residuals/model@sigma.t)
```

From the plot, we can see that the residuals are heavy tail compared with normal distribution. Jarque-Bera test and Shapiro-Wilk test also shows that. We may choose t-distribution or skewed t-distribution to improve the model.


## (4)

```{r}
library(MASS)
res_fit = fitdistr(model@residuals/model@sigma.t, "t", start = list(m=mean(model@residuals/model@sigma.t,na.rm=TRUE),s=sd(model@residuals/model@sigma.t,na.rm=TRUE), df=5), lower=c(-1, 0.001,1))
N = length(model@residuals)
quantv = (1/N)*seq(.5,N-.5,1)
qqplot(qt(quantv, res_fit$estimate[3]), model@residuals/model@sigma.t, main = 'qq plot for t-dist on residuals')
qqline(model@residuals/model@sigma.t, distribution = function(p) qt(p,res_fit$estimate[3]), probs = c(0.1, 0.9), col = 2)
```

From the plot, we can see that the fit by t-distribution is lighter tail on the right and heavy tail on the left compared with t-distribution.

## 2.

```{r}
nuest = res_fit$estimate[3]
forecasts = predict(model, n.ahead = 5)
VaR_norm = 1-exp(qnorm(0.005, forecasts$meanForecast, forecasts$standardDeviation))
VaR_t = 1-exp(forecasts$meanForecast+forecasts$standardDeviation*sqrt(nuest-2/nuest)*qt(0.005,nuest))
VaR_norm
VaR_t
```

If the residuals are normal distribution, the relative VaR is 0.01308601, but if residuals are t-distribution, relative VaR is 0.01570865, which is larger. Since from previous question, we know t-distribution is better at fitting left tails, we trust more on the second result.

## 3(1)

```{r}
summary(garchFit(~arma(1,0)+garch(1,1),data = NYSE_lret.ts,cond.dist = 'norm'))
summary(garchFit(~arma(2,0)+garch(1,1),data = NYSE_lret.ts,cond.dist = 'norm'))
summary(garchFit(~arma(3,0)+garch(1,1),data = NYSE_lret.ts,cond.dist
= 'norm'))
summary(garchFit(~arma(1,0)+garch(1,1),data = NYSE_lret.ts,cond.dist
= 'std'))
summary(garchFit(~arma(2,0)+garch(1,1),data = NYSE_lret.ts,cond.dist
= 'std'))
summary(garchFit(~arma(3,0)+garch(1,1),data = NYSE_lret.ts,cond.dist
= 'std'))
```

Based on the result, the AR(1) + GARCH(1,1) model with normally distributed innovation and the AR(2) + GARCH(1,1) model with t-distributed innovation fits best. Based on the AIC criteria, the AR(2) + GARCH(1,1) model with t-distributed innovation is better.

```{r}
model3 = garchFit(~arma(2,0)+garch(1,1),data = NYSE_lret.ts,cond.dist = 'std')
qqplot(qt(quantv,model3@fit$matcoef[7]),model3@residuals / model3@sigma.t, main = 'QQ plot for t-dist on residuals',xlab = 'Theoretical Quantiles',ylab = 'Sample Quantiles') 
qqline(model3@residuals / model3@sigma.t)

summary(model3)
```

The summary shows no autocorrelation between residuals. The qq plot also shows the t-distribution fits the innovation well. Although there is a bit skewness in residual, the shape parameter does good balance. The significance level of parameters show all parameters are useful for the model, as the p-values are just a bit above 0.1.

## (2)

```{r}
predict_argarch = predict(model3,n.ahead = 1)
1 - exp(predict_argarch$meanForecast + qt(0.005,df = model3@fit$matcoef[7]) * predict_argarch$standardDeviation)
```











