---
title: "STATS 509_HW4"
author: "Xiaoxue Xin"
date: "4876 5091"
output: word_document
---
## Problem 3(a)
```{r}
data1 = read.csv("Nasdaq_wklydata_92-12.csv", header = T) 
data2 = read.csv("SP400Mid_wkly_92-12.csv", header = T) 
index1 = which(is.na(data1$Adj.Close) == FALSE)
index2 = which(is.na(data2$Adj.Close) == FALSE)
nasq = rev(data1$Adj.Close[index1]) 
sp400 = rev(data2$Adj.Close[index2])
nasq_lgreturn = diff(log(nasq)) 
sp400_lgreturn = diff(log(sp400))
```

After we get log-return, we fit the data with multivariate normal distribution.

```{r}
mul_vect = cbind(nasq_lgreturn, sp400_lgreturn)
mean_lgreturn = signif(colMeans(mul_vect))
cov_lgreturn = signif(cov(mul_vect))
mean_lgreturn
cov_lgreturn
```
```{r}
library(copula)
library(fGarch)
library(MASS)
library(fCopulae)

```


```{r}
est.nasq = as.numeric(fitdistr(nasq_lgreturn, "normal")$estimate)
est.sp400 = as.numeric(fitdistr(sp400_lgreturn, "normal")$estimate)
dat1 = cbind(pnorm(nasq_lgreturn, mean = est.nasq[1], sd = est.nasq[2]), pnorm(sp400_lgreturn, mean = est.sp400[1], sd = est.sp400[2]))
ft1 = fitCopula(data = dat1, copula = normalCopula(0.3, dim = 2), optim.method = "BFGS", start = 0.5)
summary(ft1)
```

Next, we draw QQ-plot to see the whether fit is good or not.

```{r}
par(mfrow = c(1,2))
qqnorm(nasq_lgreturn, main = "Nasdaq-log return")
qqline(nasq_lgreturn)
qqnorm(sp400_lgreturn, main = "SP400-log return")
qqline(sp400_lgreturn)
```

From the QQ-plot, we can see that there are heavy-tail compared with normal distribution. Next, we draw a plot comparing the empirical vs. theoretical bivariate cumulative distribution function.

```{r}
u1 = dat1[,1]
u2 = dat1[,2]
dem = pempiricalCopula(u1, u2)
contour(dem$x, dem$y, dem$z, main = "Empirical-Gaussian", col = 'blue', lty = 1, lwd = 2, nlevel = 20)
cn = normalCopula(ft1@estimate[1], dim = 2, dispstr = "un")
utdis = rCopula(100000, cn)
demt = pempiricalCopula(utdis[,1], utdis[,2])
contour(demt$x, demt$y, demt$z, main = "Gauss", col = 'red', lty = 2, lwd = 2, add = TRUE, nlevel = 20)
```

From the above plot, we can see that the difference between two cdf functions is obvious. The multivariate normal distribution fit is not very good.

## (b)
We will use multivariate t distribution to fit the data. First, we find the mean, scale, and degree of freedom.
Next, we need to convert the data to standard deviation for incorporating within "pstd".

```{r}
est.nasqt = as.numeric(fitdistr(nasq_lgreturn,"t")$estimate)
est.sp400t = as.numeric(fitdistr(sp400_lgreturn,"t")$estimate)
est.nasqt[2] = est.nasqt[2] * sqrt(est.nasqt[3] / (est.nasqt[3]-2))
est.sp400t[2] = est.sp400t[2] * sqrt(est.sp400t[3] / (est.sp400t[3]-2))
dat2 = cbind(pstd(nasq_lgreturn, mean = est.nasqt[1], sd = est.nasqt[2], nu = est.nasqt[3]), pstd(sp400_lgreturn, mean = est.sp400t[1], sd = est.sp400t[2], nu = est.sp400t[3]))
N = length(nasq_lgreturn)
quantv = (1/N)*seq(0.5, N - 0.5, 1)
par(mfrow = c(1,2))
qqplot(sort(nasq_lgreturn), qt(quantv, est.nasqt[3]), main = 'Nasdaq - QQ plot for t-dist')
abline(lm(qt(c(0.25, 0.75), est.nasqt[3]) ~ quantile(nasq_lgreturn, c(0.25, 0.75))))
qqplot(sort(sp400_lgreturn), qt(quantv, est.sp400t[3]), main = 'SP400 - QQ plot for t-dist')
abline(lm(qt(c(0.25, 0.75), est.sp400t[3])~quantile(sp400_lgreturn, c(0.25, 0.75))))
```

From  QQ plots, we can see that the fitting of t-distribution is better than normal distribution.

```{r}
cor_tau = cor(nasq_lgreturn, sp400_lgreturn, method = "spearman")
omega = cor_tau
cop_t_dim2 = tCopula(omega, dim = 2, dispstr = "un", df = 4)
ft2 = fitCopula(cop_t_dim2, optim.method = "L-BFGS-B", data = dat2)
summary(ft2)
```

The estimation of degree of freedom is 3.8299.

```{r}
u1 = dat2[,1]
u2 = dat2[,2]
dem = pempiricalCopula(u1,u2)
contour(dem$x, dem$y, dem$z, main = "Empirical-t", col = 'blue', lty = 1, lwd = 2, nlevel = 20)
ct = tCopula(ft2@estimate[1], dim = 2, dispstr = "un", df = ft2@estimate[2]) 
utdis = rCopula(100000, ct)
demt = pempiricalCopula(utdis[,1], utdis[,2])
contour(demt$x, demt$y, demt$z, main = "t",
        col = 'red', lty = 2, lwd = 2, add = TRUE, nlevel = 20)
```
From the plot, we can see that the estimation is better than the multivariate normal distribution fitting.
Next, we derive a confidence interval for the degrees of freedom via the method of profile likelihood. 

```{r}
library(mnormt)
df = seq(1, 8, 0.01)
n = length(df)
loglik_max = rep(0, n)
for(i in 1:n){
  fit = cov.trob(mul_vect, nu = df[i])
  mu = as.vector(fit$center)
  sigma = matrix(fit$cov, nrow = 2)
  loglik_max[i] = sum(log(dmt(mul_vect, mean = fit$center, S = fit$cov, df = df[i])))
  }
plot(df, loglik_max, xlab = 'nu', ylab = 'Profile-likelihood function')
nuest = df[which.max(loglik_max)]
nuest
position = which((loglik_max[which.max(loglik_max)]-loglik_max) <= 0.5*qchisq(0.95, 1))
lower_bound = df[position[1]]
upper_bound = df[position[length(position)]]
lower_bound
upper_bound
```

By using profile likelihood estimation, we get the estimation of degree of freedom is 2.8 with confidence interval [2.44, 3.25].

## (c)
```{r}
AIC_gauss = -2*ft1@loglik+2*1
AIC_t = -2*ft2@loglik+2*2
AIC_gauss
AIC_t
```

Based on AIC criteria, we may choose model with minimized AIC value. So, we need to choose t-distribution fitted model. And from QQ-plot and plot comparing the empirical vs.  theoretical bivariate cumulative distribution function, the t-distribution fitted model is better than normal distribution.

Thus, based on (a) and (b), I prefer the second model. The QQ-plot for the second model is better. And the plot comparing the empirical vs. theoretica also fits better in the second model.
## (d)

For the model derived in (a), we have

```{r}
cn = normalCopula(ft1@estimate[1], dim = 2, dispstr = "un")
uvsim1 = rCopula(1000000, cn)
data_sim1 = cbind(qnorm(uvsim1[,1], mean = est.nasq[1], sd = est.nasq[2]),qnorm(uvsim1[,2], mean = est.sp400[1], sd = est.sp400[2]))
data1 = 0.5 *data_sim1[,1] + 0.5 * data_sim1[,2]
VaR1 = -quantile(data1, 0.001) * 10^7
VaR1
```

The VaR is 886358.7.

For the model derived in (b), we have
```{r}
uvsim = rCopula(1000000, ct)
data_sim = cbind(qstd(uvsim[,1], mean = est.nasqt[1], sd = est.nasqt[2], nu = est.nasqt[3]), qstd(uvsim[,2], mean = est.sp400t[1], sd = est.sp400t[2], nu = est.sp400t[3]))
datat = 0.5 *data_sim[,1] + 0.5 * data_sim[,2]
VaR = -quantile(datat, 0.001) * 10^7
VaR
```

The VaR is 1591786.

## (e)

```{r}
set.seed(2015)
ct = tCopula(ft2@estimate[1], dim = 2, dispstr = "un", df = ft2@estimate[2])
uvsim = rCopula(100000, ct)
w = seq(0, 1, 0.01)
n = length(w)
VaRv = rep(0, n)
expected_return = rep(0,n)
varian=rep(0,n)
data_sim = cbind(qstd(uvsim[,1], mean = est.nasqt[1], sd = est.nasqt[2], nu = est.nasqt[3]),qstd(uvsim[,2], mean = est.sp400t[1], sd = est.sp400t[2], nu = est.sp400t[3]))
for(i in 1:n)
{
  datat = w[i]*data_sim[,1]+(1-w[i])*data_sim[,2]
  VaRv[i] = -quantile(datat,0.002)
  expected_return[i] = mean(datat)
  varian[i] = sd(nasq_lgreturn)^2*w[i]^2+sd(sp400_lgreturn)^2*(1-w[i])^2+2*sd(nasq_lgreturn)*sd(sp400_lgreturn)*cor(nasq_lgreturn,sp400_lgreturn)*w[i]*(1-w[i])
}
# Maximun expected return
w_exp = w[which.max(expected_return)]
expected_final = expected_return[which.max(expected_return)]*1e7
w_exp
expected_final
# Minimum volatility
w_var = w[which.min(varian)]
var_final = varian[which.min(varian)]
w_var
var_final
# Minimum VaR at q = 0.002
w_VaR = w[which.min(VaRv)]
VaR_final = VaRv[which.min(VaRv)]*1e7
w_VaR
VaR_final
```
For Multivariate t-distribution: According to the result, w for maximum expected return is 1 and corresponding expected return is 34391.31. w for min volatility is 0 and corresponding variance is 0.0007528559. w for min VaR is 0.045 and corresponding VaR is 1228242.

```{r}
set.seed(2015)
uvsim = rCopula(100000, cn)
w = seq(0, 1, 0.01)
n = length(w)
VaRv = rep(0, n)
expected_return = rep(0,n)
varian=rep(0,n)
data_sim2 = cbind(qnorm(uvsim[,1], mean = est.nasq[1], sd = est.nasq[2]),qnorm(uvsim[,2], mean = est.sp400[1], sd = est.sp400[2]))
for(i in 1:n)
{
  datat = w[i]*data_sim2[,1]+(1-w[i])*data_sim2[,2]
  VaRv[i] = -quantile(datat,0.002)
  expected_return[i] = mean(datat)
  varian[i] = sd(nasq_lgreturn)^2*w[i]^2+ sd(sp400_lgreturn)^2*(1-w[i])^2+2*sd(nasq_lgreturn)*sd(sp400_lgreturn)*cor(nasq_lgreturn,sp400_lgreturn)*w[i]*(1-w[i])
}
# Maximun expected return
w_exp = w[which.max(expected_return)]
expected_final = expected_return[which.max(expected_return)]*1e7
w_exp
expected_final
# Minimum volatility
w_var = w[which.min(varian)]
var_final = varian[which.min(varian)]
w_var
var_final
# Minimum VaR at q = 0.002
w_VaR = w[which.min(VaRv)]
VaR_final = VaRv[which.min(VaRv)]*1e7
w_VaR
VaR_final
```

For Multivariate normal-distribution: According to the result, w for maximum expected return is 0 and corresponding expected return is 18275.44. w for min volatility is 0 and corresponding variance is 0.0007528559. w for min VaR is 0.017 and corresponding VaR is 777184.3.










