---
title: "STATS509_HW8"
author: "Xiaoxue Xin"
date: "4876 5091"
output: word_document
---

```{r}
library(Ecdat)
data("CRSPday")
crsp = CRSPday[,7]
arima1 = arima(crsp, order = c(1,0,0))
arima1
arima2 = arima(crsp, order = c(2,0,0))
arima2
```

Since the AIC of AR(1) is less than AR(2), I prefer AR(1) model.

```{r}
low = arima1$coef[1] + sqrt(arima1$var.coef[1,1])*qnorm(0.025)
up = arima1$coef[1] + sqrt(arima1$var.coef[1,1])*qnorm(0.975)
low
up
```

The 95% confidence interval of alpha in AR(1) is (0.04646222, 0.1241414)


```{r}
tsdiag(arima1)
tsdiag(arima2)
```

From diagnostic plots, we can see that there is slight difference between two models, so adding a lag doesn't improve the model much. We still prefer AR(1). We can also see the residuals of two models are almost white noise and stationary. 

```{r}
myqqnorm <- function(x){
  qqnorm(x)
  qqline(x)
}
myqqnorm(arima1$residuals)
myqqnorm(arima2$residuals)
```

From QQ-plots, we can see that the residuals of two models are heavy-tail relative to normal distribution which may conflict with assumption that the residuals are normal distributed.


```{r}
library(forecast)
MA = auto.arima(crsp, seasonal = FALSE, max.p = 5, max.q = 5, ic = 'aic')
MA
tsdiag(MA)
myqqnorm(MA$residuals)
```

Using AIC criteria, we choose MA(1) model to fit the data. From the QQ-plot, we can see that the residuals are heavy-tail relative to normal distribution. From the diagnostic plots, we can see that there is little difference between MA(1) and AR(1), AR(2), but the AIC of MA(1) is a little less than AR(1) and AR(2).





